\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{ {images/} }
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Controller Area Network Protocol\\ for Vehicle System\\
{\footnotesize }
\thanks{University of Applied Sciences Hamm-Lippstadt.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Sheikh Muhammad Adib Bin Sh Abu Bakar}
\IEEEauthorblockA{\textit{Hochshule Hamm-Lippstadt} \\
\textit{B.Eng. Electronic Engineering}\\
Lippstadt, Germany \\
sheikh-muhammad-adib.bin-sh-abu-bakar@stud.hshl.de}

\and
\IEEEauthorblockN{2\textsuperscript{nd} Zafirul Izzat Bin Mohamad Zaidi}
\IEEEauthorblockA{\textit{Hochshule Hamm-Lippstadt} \\
\textit{B.Eng. Electronic Engineering}\\
Lippstadt, Germany \\
zafirul-izzat-bin.mohamad-zaidi@stud.hshl.de}

\and
    \IEEEauthorblockN{}
\IEEEauthorblockA{\textit{} \\
\textit{------------------------------------}\\
 \\
}

\and
    \IEEEauthorblockN{3\textsuperscript{rd} Muhammad Farid Izwan Bin Mohamad Shabri}
\IEEEauthorblockA{\textit{Hochshule Hamm-Lippstadt} \\
\textit{B.Eng. Electronic Engineering}\\
Lippstadt, Germany \\
muhammad-farid-izwan.bin-mohamad-shabri@stud.hshl.de}

\and
    \IEEEauthorblockN{}
\IEEEauthorblockA{\textit{} \\
\textit{------------------------------------}\\
 \\
}


}


\maketitle


\input{abstract.tex}
\input{introduction.tex}
\input{type.tex}
\input{problem.tex}
\input{can.tex}
\input{application.tex}
\input{state.tex}
\input{discuss_n_conclusion}

\section*{Acknowledgment}

We would like to express our very great appreciation to Prof. Dr.-Ing.  João Paulo Javidi da Costa  for his valuable and constructive suggestions during the planning and development of this project. His willingness to give his time so generously has been very much appreciated.


\begin{thebibliography}{00}
\bibitem{b1} B. Galloway and G. P. Hancke, "Introduction to Industrial Control Networks," in IEEE Communications Surveys & Tutorials, vol. 15, no. 2, pp. 860-880, Second Quarter 2013, doi: 10.1109/SURV.2012.071812.00124. 
\bibitem{b2}  J. Wu, “ECE Senior Capstone Project,” How Bluetooth Works, 2017. 
\bibitem{b3}  M. Sparkes, “What does Wi-Fi Stand For?,” New Scientist, 2011. [Online]. Available: https://www.newscientist.com/question/what-does-wi-fi-stand-for/. [Accessed: 24-May-2022]. 
\bibitem{b4}  S. Campbell, “Basics of Uart Communication,” Circuit Basics, 14-Nov-2021. [Online]. Available: https://www.circuitbasics.com/basics-uart-communication/. [Accessed: 24-May-2022]. 
\bibitem{b5}  F. Ahmad, M. Sultan (Eds.) Technology in Agriculture. London, United Kingdom, IntechOpen, 2021 [Online]. Available from: https://www.intechopen.com/books/10454 doi: 10.5772/intechopen.92469
\bibitem{b6} L. B. Fredriksson, “Medical: Kvaser: Advanced can solutions,” Kvaser, 15-Jun-2020. [Online]. Available: https://www.kvaser.com/about-us/applications/medical/. [Accessed: 26-May-2022].
\bibitem{b7} C. S. amp; Webinar, “Vending vehicle with robot making coffee,” Applications, 2022. [Online]. Available: https://can-newsletter.org/engineering/applications/180813-vending-vehicle-with-robot-making-coffee-pix. [Accessed: 26-May-2022].

\end{thebibliography}


%\bibliographystyle{plain-annote}
%\bibliography{reference_latex/ref} 







\end{document}
